---
title: "Getting Started"
author: "Aimee Gott"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

*This is a simple example of including a package vignette. Using RMarkdown allows us to generate HTML package documentation. RMarkdown is a simple to use mark-up language.* 

## Loading the package

After installing we can load the package in the usual manner for a package as can be seen in the example:

```{r}
library(summaryTools)
```

## Main Function

The main package function is `numericSummary`. We provide a numeric vector and it will return a named vector containing:

* Min
* Mean
* Variance
* Max
* NAs

Take a look at the following example:

```{r}
exampleData <- c(5, 9, 11, 13, NA, 2, 4, 8, 3)
stats <- numericSummary(exampleData)
stats
```

## Uses

We can use these summary statistics to generate simple graphics to visualise the information.

```{r, fig.show='hold'}
plot(exampleData)
abline(h = stats["Mean"], col = "grey", lty = 2)
```


